---
title: "ABG Portifolio test"
output:
   html_document:
    highlight: textmate
    number_sections: no
    theme: flatly
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
runtime: shiny
resource_files:
- ABG_Port.Rproj
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(here)
library(tidyverse)
library(readxl)
library(kableExtra)
library(plotly)
library(glue)
library(readr)
library(ggplot2)
library(dplyr)
#library(png)
#library(jpeg)
#library(magick)
```

# Introduction

## What is the Appleseed Community?

```{r, warning = FALSE, message = FALSE, echo = FALSE}

library(jpeg)

jj <- readJPEG("Test_Banner.jpeg",native=TRUE)
plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
rasterImage(jj,0,0,1,1)


```

This document is just a suggestion of portfolio basic design

Who are we?

What are FC1?

&nbsp;
&nbsp;
  
## What do we like to do?


More text, More text,More text

More text, More text,More text
  
More text, More text,More text

More text, More text,More text

&nbsp;
&nbsp;

# Big Projects

Events

Akina, Akagi, minigames, FC1, Offseason, etc.
  

## Akina

Insert Image here
Link for Akina, click down

[Akina Video ](https://www.youtube.com/watch?v=moPjqLGlNQ8)


&nbsp;
&nbsp;

# Team

Who we are...

## The CEOs

### About Adam

The founder

Insert Image
  
More text, More text,More text

More text, More text,More text

### Akira

HR Management 

Insert Image
  
More text, More text,More text

More text, More text,More text

### Laser

Coder Manager and a boat racer star

Insert Image
  
More text, More text,More text

More text, More text,More text


## The Staff Members

More text, More text,More text

More text, More text,More text
  
More text, More text,More text

More text, More text,More text






